No Detectable Evidence of Genetic Associations with Anadromous and Resident Masu Salmon Sampled within Hokkaido

### 2022-06-01 paper/paper_draft.Rmd
added the fixed, knitted paper draft since it wasn't knitting correctly for Audrey

```{r, eval=TRUE, include=FALSE}
mat <- read.table("../angsdput.covMat")
IBS <- data.table::fread("../angsdput.covMat")
IBS.loci <- data.table::fread("../data/angsdput.ibs.gz")
nrow(IBS)
IBS <- IBS[-32,-c(97, 32)]
pca_r <- eigen(IBS)
pca <- pca_r$vectors
write.table(pca[,1:20], "pca20.txt", col.names = FALSE, row.names = FALSE, quote=FALSE, sep="\t")
colnames(pca) <- paste0("PC", 1:ncol(pca))
meta <- read.table("../data/sample_meta.txt", header = TRUE)[-32,]
pca <- cbind(pca, meta)

@@

```{r Figure_1_print,echo=FALSE,warning=FALSE, include=TRUE,fig.cap="Figure 1: Association across the genome with migratory status showing that no loci were found that were significantly associated with the given traits (anadromy and residency)",fig.width=7, fig.height=4, fig.align='center', fig.cap.style="Image Caption"}
figure_1$plot

@@

```{r Figure_2_print,echo=FALSE,warning=FALSE,include=TRUE,fig.cap="Figure 2: PCA plot showing the relatedness between anadromous and resident individuals in TK and CH populations",fig.width=7, fig.height=4, fig.align='center', fig.cap.style="Image Caption"}
p1

>>>>

```{r, eval=TRUE, include=FALSE}
# mat <- read.table("../angsdput.covMat")
IBS <- data.table::fread("../angsdput.covMat")
IBS.loci <- data.table::fread("../data/angsdput.ibs.gz")
nrow(IBS)
IBS <- IBS[-32,-c(97, 32)]
pca_r <- eigen(IBS)
pca <- pca_r$vectors
write.table(pca[,1:20], "pca20.txt", col.names = FALSE, row.names = FALSE, quote=FALSE, sep="\t")
colnames(pca) <- paste0("PC", 1:ncol(pca))
meta <- read.table("../data/sample_meta.txt", header = TRUE)[-32,]
pca <- cbind(pca, meta)

@@

```{r Figure_1_print,echo=FALSE,warning=FALSE,eval=TRUE,include=TRUE,fig.cap="Figure 1: Association across the genome with migratory status showing that no loci were found that were significantly associated with the given traits (anadromy and residency)",fig.width=7, fig.height=4, fig.align='center', fig.cap.style="Image Caption"}
figure_1$plot

@@

```{r Figure_2_print,echo=FALSE,warning=FALSE,eval=TRUE,include=TRUE,fig.cap="Figure 2: PCA plot showing the relatedness between anadromous and resident individuals in TK and CH populations",fig.width=7, fig.height=4, fig.align='center', fig.cap.style="Image Caption"}
p1
